MADA Data Analysis Project

### 2021-10-09 products/manuscript/Manuscript.Rmd
Data Exploration Commit (07)

## Data import and cleaning
_Write code that reads in the file and cleans it so it's ready for analysis. Since this will be fairly long code for most datasets, it might be a good idea to have it in one or several R scripts. If that is the case, explain here briefly what kind of cleaning/processing you do, and provide more details and well documented code somewhere (e.g. as supplement in a paper). All materials, including files that contain code, should be commented well so everyone can follow along._

>>>>

## Data import and cleaning

Data comes out of different reports. This report is added to a supplemental report gathered while the samples were processed and added into one giant compilation then read into R.

processingscript.R was modified to do initial cleaning and preparation of the dataset for further exploration.Data is also saved.
